Proposed Solution

### 2016-01-29 system.tex
random

Before describe how our system for learning rules is working, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on already given set of basic types. However, typing is also a system module than can be easily extended to support
more types. In that case the user will need to provide rules for type inference and probability

@@

Typing the untyped expressions appearing in configuration files 
is the first step in parsing and translating the data. 
Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
variable name and $v$ denotes variable value. However, based only on the 
value $v$ we cannot determine the type of $n$.

@@

Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$ 
and $\Sigma p_i = 1$.

Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
This is an issue when we try to learn relational rules between keywords. 
Take the following file in the learning

We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.

>>>>

Before describing how our system for learning rules works, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on an
already given set of basic types. However, typing is also a system module than can be easily extended to support
more types. In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.

@@

Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
variable name and $v$ denotes variable value. However, based only on the 
value $v$ we cannot determine the type of $n$.

@@

Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
$0 \le p_i \le 1$ 
and $\Sigma p_i = 1$. These probabilities are learned from the training 
corpus.

When a value has a quantum type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a quantum type 
(e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
we now generate rules for strings and integers.

For a given value, its quantum type is updated over time. When the
